Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-02-03 main.tex
Update on Overleaf.

\begin{remark}\label{remark:fullrecursivesum:exterior}
    Recall that the potential $w$ for the gradient $\cartan u$ satisfies the recursive estimate 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
        \| \cartan u      \|_{L^{p}(T_{m})} 
        \\&\qquad
        +
        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
        \Cfivetrafo{n}{k+1}{\ell_{m}}{p}(\calT)
%         \Cfiveprime{n}{k}(\calT)^{k} 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
        \\&\qquad
        + 
        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT) 
%         \Cfiveprime{n}{k}(\calT)^{k-1} 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(\Makoto_{m-1})}
        .
    \end{align*}
    Unwrapping the recursion for the norm over the $m$-th simplex, 
    we find an estimate of the form 
    \begin{align}\label{math:fullrecursivesum:exterior}
        \| w \|_{L^{p}(T_{m})} 
        &
        \leq 
        \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}
        .
    \end{align}
    Here, $C_{m,\ell}$ is the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        % \\&
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \sum_{\ell=0}^{M} 
        \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
        \right)
        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
        ,
    \end{align*}
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
\end{remark}

@@

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio       & $\grad$ est  & $\grad$ ratio  \\
        \hline
        $\calT_{C,5}$   & 0.317        & 4.317        & 13.581              & 3.246        & 10.214         \\
        \hline
        $\calT_{C,K}$   & 0.317        & 3.571        &  11.23              & 11.034       & 34.722         \\
        \hline
        $\calT_{B,5}$   & 1.022        & 7.698        & 7.5285              & 25.972       & 25.397         \\
        \hline
        $\calT_{B,K}$   & 1.022        & 10.106       & 9.8824              & 53.763       & 52.573         \\
        \hline
        $\calT_{F}$     & 0.711        & 10.622       & 14.927              &  268.071     & 377.033        \\ 
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]  
    \color{red}
    \centering
    \begin{tabular}{|r||r|r|r||r|r|r|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio          & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310506212          & 0.183             & 3.391             & 18.453          \\
        \hline
        $\calT_{C,K}$   & 0.225        & 12.157      & 54.0308334194          & 0.183             & 25.899            & 140.920         \\
        \hline
        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056871148          & 0.233             & 152.886           & 655.993         \\
        \hline
        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655711308          & 0.233             & 512.273           & 2198.026        \\
        \hline
        $\calT_{F}$     & 0.554        & 25752.342   & 46403.3023359          & 0.310             & 8958.467          & 28835.266       \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}

>>>>

\begin{comment}
\begin{remark}\label{remark:fullrecursivesum:exterior}
    Recall that the potential $w$ for the gradient $\cartan u$ satisfies the recursive estimate 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
        \| \cartan u      \|_{L^{p}(T_{m})} 
        \\&\qquad
        +
        C_{\PF,T_{m},\Gamma_{m},k,p}(\calT) 
        \Cfivetrafo{n}{k+1}{\ell_{m}}{p}(\calT)
%         \Cfiveprime{n}{k}(\calT)^{k} 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| \cartan u \|_{L^{p}(\Makoto_{m-1})}
        \\&\qquad
        + 
        \Cfivetrafo{n}{k}{\ell_{m}}{p}(\calT) 
%         \Cfiveprime{n}{k}(\calT)^{k-1} 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(\Makoto_{m-1})}
        .
    \end{align*}
    Unwrapping the recursion for the norm over the $m$-th simplex, 
    we find an estimate of the form 
    \begin{align}\label{math:fullrecursivesum:exterior}
        \| w \|_{L^{p}(T_{m})} 
        &
        \leq 
        \sum_{\ell=0}^{M} C_{m,\ell} \| \cartan u \|_{L^{p}(T_{\ell})}
        .
    \end{align}
    Here, $C_{m,\ell}$ is the coefficient of $\| \cartan u \|_{L^{p}(T_{\ell})}$, possibly zero, 
    as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        % \\&
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \sum_{\ell=0}^{M} 
        \| \cartan u \|_{L^{p}(T_{\ell})}^{p} 
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
        \right)
        \| \cartan u \|_{L^{p}(\Omega)}^{p} 
        ,
    \end{align*}
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
\end{remark}
\end{comment}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio       & $\grad$ est  & $\grad$ ratio  \\
        \hline
        $\calT_{C,5}$   & 0.317        & 4.317        & 13.581              & 3.246        & 10.214         \\
        \hline
        $\calT_{C,K}$   & 0.317        & 3.571        &  11.23              & 11.034       & 34.722         \\
        \hline
        $\calT_{B,5}$   & 1.022        & 7.698        & 7.5285              & 25.972       & 25.397         \\
        \hline
        $\calT_{B,K}$   & 1.022        & 10.106       & 9.8824              & 53.763       & 52.573         \\
        \hline
        $\calT_{F}$     & 0.711        & 10.622       & 14.927              &  268.071     & 377.033        \\ 
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]  
    \centering
    \begin{tabular}{|r||r|r|r||r|r|r|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio          & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310                & 0.183             & 3.391             & 18.453          \\
        \hline
        $\calT_{C,K}$   & 0.225        & 12.157      & 54.030                 & 0.183             & 25.899            & 140.920         \\
        \hline
        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056                & 0.233             & 152.886           & 655.993         \\
        \hline
        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655                & 0.233             & 512.273           & 2198.026        \\
        \hline
        $\calT_{F}$     & 0.554        & 25752.342   & 46403.302              & 0.310             & 8958.467          & 28835.266       \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=1$ (3rd and 4th column) and with $k=2$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}
